A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-06 paper.tex
Adding more figures

\usepackage[pdftex]{graphicx}
\graphicspath{{./png/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}

@@

Two convenient ways of modifying the non-membership function and
satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the non-membership function,
as is depicted in \ref{ifs}; and 2) one can set different means and
standard deviations of the Gaussian membership and non-membership
functions, but the $height$ of the membership function must be equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. To clarify, the $height$
of the membership function ($h_{mf}$) of an IFS is equal to
$max(\mu(x))$, and the $height$ of the non-membership function
($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

%\ref{ifs-diff-mu-sd}

@@

>>>>

\usepackage[pdftex]{graphicx}
\graphicspath{{./png/}{./eps/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}

@@

Two convenient ways of modifying the non-membership function and
satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the non-membership function,
as is depicted in \ref{ifs}; and 2) one can set different means and
standard deviations of the Gaussian membership and non-membership
functions, but the $height$ of the membership function must be equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. An example of the latter
case is shown in Fig. \ref{ifs-diff-mu-sd}.To clarify, the $height$
of the membership function ($h_{mf}$) of an IFS is equal to
$max(\mu(x))$, and the $height$ of the non-membership function
($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

The first step

@@

\begin{figure}[!t]
  \centering
  \includegraphics[height=2.5in]{proposed-method-flow-chart}
  \caption{Proposed Method Flow Chart}
  \label{flow-chart}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{alpha-cut}
  \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
  \label{alpha-cut}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs-union}
  \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
  \label{ifs-union}
\end{figure}
